Xolotl: An Intuitive and Approachable Neuron \& Network Simulator in MATLAB

### 2018-05-29 PaperLatex/paper.tex
Clarify language in figure captions

\begin{figure}
	\centering
	\includegraphics[width=1.0\linewidth]{gfx/figure_network}
	\caption{Simulating a network of conductance-based model neurons. (A) Diagram of a network model of the pyloric rhythm in the crustacean stomatogastric ganglion (Prinz \textit{et al.} 2004). (B) Hierarchical structure of a neuronal network considers compartments as components of the network and conductances and synapses as components of compartments. (C) \textit{xolotl} implements conductances as fields of compartments and synapses as connections between compartments. (D-F) Simulated voltage trace of a model network for the three compartments. (G) Time series of synaptic currents in the simulated network are outputs of the integration. Two cholinergic (chol) current traces are plotted.}
	\label{fig:figurenetwork}
\end{figure}

>>>>

\begin{figure}
	\centering
	\includegraphics[width=1.0\linewidth]{gfx/figure_network}
	\caption{Simulating a network of conductance-based model neurons. (A) Diagram of a network model of the pyloric rhythm in the crustacean stomatogastric ganglion (Prinz \textit{et al.} 2004). (B) Each neuron is modeled as a single compartment with 7-8 intrinsic conductances and 1-3 post-synaptic conductances. (C) \textit{xolotl} implements conductances as fields of compartments and synapses as connections between compartments. (D-F) Simulated voltage trace of a model network for the three compartments. (G) Time series of synaptic currents in the simulated network can be obtained from the integration.}
	\label{fig:figurenetwork}
\end{figure}
